Current Sheet Theory

### 2024-05-24 index.qmd
update
chore: refactor

---
title: "Current Sheet Theory"
code-links:
  - repo
  - text: Tana
    href: https://app.tana.inc?nodeid=OzzX0sVA4_6X
  - text: Zotero
    href: zotero://select/library/collections/DZHNUFNV
---

@@

We are interested in solutions with $B_x^2 + B_y^2 = B_0^2 = const$ (force-free current sheet). From Ampere's law (@eq-Jx) and (@eq-Jy), we have:

@@

$C_1=0$ immediately implies $θ = θ_1 + k \pi$ and $Λ_x=Λ_y$.

@@

  $$
  u_1 = \pm \frac{B_0 Γ_1}{B_z n_1}
  $$

@@

@@

Given $c = 1/\sqrt{2}$, we have $B_y \to 0$ as $z \to \infty$. Profiles are plotted below.

@@

```mathematica
Manipulate[
 Block[{B0 = B0i, c = ci},
  p1 = Plot[
    Evaluate[{n[z], Bx[z], By[z], u1x[z], u1y[z]} /. sols //. 
      rulesn],
    {z, -zmax, zmax},
    PlotLegends -> {n, Subscript[B, x], Subscript[B, y], Subscript[u, 
      x], Subscript[u, y]}];
  Export["figures/profiles.jpg", p1];
  ],

@@

## Questions

- Why not motionless electrons?

>>>>

---
title: "Current Sheet Theory"
code-links:
  - text: Tana
    href: https://app.tana.inc?nodeid=OzzX0sVA4_6X
  - text: Zotero
    href: zotero://select/library/collections/DZHNUFNV
---

@@

We are interested in solutions with $B_x^2 + B_y^2 = B_0^2 = const$ (force-free current sheet). This provides another equation for the system, now we have 3*2+2+1=9 equations for 10 unknowns (the system is close to be fully determined). From Ampere's law (@eq-Jx) and (@eq-Jy), we have:

@@

$C_1=0$ immediately implies $θ = θ_1 + k \pi$ and $Λ_x=Λ_y$. #TODO: Prove $C_1=0$ is like a boundary condition not a equation.

@@

  $$
  u_1 = \pm \frac{B_0 Γ_1}{B_z n_1(\infty)}
  $${#eq-u1}

@@

The system $S$ could be fully determined by $λ_n, λ_z, c, B_0$ parameters, provided $n(z)$ profiles.

$$S=S(z; n(z); λ_n, λ_z, c, B_0)$$

@@

Given $c = 1/\sqrt{2}$, we have $B_y \to 0$ as $z \to \infty$. Profiles are plotted below for $B_0 = 2$.

@@

```mathematica
Manipulate[
 Block[{B0 = B0i, c = ci},
  p1 = Plot[
    Evaluate[{n[z], Bx[z], By[z], u1x[z], u1y[z]} /. sols //. rulesn],
    {z, -zmax, zmax},
    PlotLegends -> {n, Subscript[B, x], Subscript[B, y], Subscript[u, x], Subscript[u, y]}
  ];
  Export["figures/profiles.jpg", p1];
  p1
  ],

@@
